### 2022-06-24 README.Rmd
change papaja to CRAN version
update 2022-06-23 18:40:38
update 2022-06-24 22:22:21

``` r
remotes::install_github("crsh/papaja", dependencies = TRUE, update = "never")

@@

> Van Lissa, C. J., Brandmaier, A. M., Brinkman, L., Lamprecht, A., Peikert, A., , Struiksma, M. E., & Vreede, B. (in press). WORCS: A Workflow for Open Reproducible Code in Science. Data Science, 2021. Data Science, vol. 4, no. 1, pp. 29-49. DOI: 10.3233/DS-210031.

@@

## Adoption of WORCS by users

```{r, echo = FALSE, message=FALSE, warning=FALSE}
library(gh)
library(dlstats)
dl <- dlstats::cran_stats("worcs")
dl <- sum(dl$downloads)

worcs_repo <- gh("/repos/cjvanlissa/worcs")

repos <- gh("GET /search/code", username = "cjvanlissa", q="worcs_version filename:.worcs")

worcs_repos <- data.frame(t(sapply(repos[["items"]], function(x){
  c(owner = x$repository$owner$login,
    name = x$repository$name,
    url = x$repository$html_url
  )
})))

worcs_repos <- worcs_repos[!((worcs_repos$owner %in% c("cjvanlissa", "cran") & worcs_repos$name == "worcs")| grepl("(penguin|\\btmp|demo|test)", tolower(worcs_repos$name))), ]

tmp <- paste0(sapply(unique(worcs_repos$owner), function(x){
  owner_repos <- worcs_repos[worcs_repos$owner == x, , drop = FALSE]
  paste0("\n    - ", x, "  ",
         paste0("\n        + [", owner_repos$name, "](", owner_repos$url, ")  ", collapse = ""))
  }),
  collapse = "")

invited <- read.table("https://raw.githubusercontent.com/cjvanlissa/resume/master/invited.csv", sep = ",", header = TRUE)
invited <- invited[grepl("(worcs|workflow)", tolower(invited$Topic)), c("Institute", "Year", "City", "Country", "Date")]
invited <- paste0(apply(invited, 1, function(x){paste0("\n    - ", x[1], " (", x[2], ")  ")}), collapse = "")
```

As of `r Sys.Date()`, these are indicators of the adoption of `worcs` by users:

1. The preprint has been downloaded 1372 times, since being published on 31-05-2020
1. The paper in [Data Science](https://content.iospress.com/articles/data-science/ds210031) has been cited 13 times
1. The `worcs` R-package has been downloaded `r dl` times from CRAN, since being published on 18-05-2020
1. The GitHub project has been forked `r worcs_repo$network_count` times, watched `r worcs_repo$subscribers_count` times, and starred `r worcs_repo$watchers` times
1. The lead author has given invited lecturegs on WORCS at:`r invited`
1. WORCS is currently used in the following public itHub repositories (sorted by user):`r tmp`

>>>>

``` r
install.packages("papaja", dependencies = TRUE, update = "never")

@@

> Van Lissa, C. J., Brandmaier, A. M., Brinkman, L., Lamprecht, A., Peikert, A., , Struiksma, M. E., & Vreede, B. (2021). WORCS: A Workflow for Open Reproducible Code in Science. Data Science. Data Science, vol. 4, no. 1, pp. 29-49. DOI: 10.3233/DS-210031.

@@

<!-- ## Adoption of WORCS by users -->

```{r, eval = FALSE, echo = FALSE, message=FALSE, warning=FALSE}
library(gh)
library(dlstats)
dl <- dlstats::cran_stats("worcs")
dl <- sum(dl$downloads)

# worcs_repo <- gh("/repos/cjvanlissa/worcs")
# 
# repos <- gh("GET /search/code", username = "cjvanlissa", q="worcs_version filename:.worcs")
# 
# worcs_repos <- data.frame(t(sapply(repos[["items"]], function(x){
#   c(owner = x$repository$owner$login,
#     name = x$repository$name,
#     url = x$repository$html_url
#   )
# })))

# worcs_repos <- worcs_repos[!((worcs_repos$owner %in% c("cjvanlissa", "cran") & worcs_repos$name == "worcs")| grepl("(penguin|\\btmp|demo|test)", tolower(worcs_repos$name))), ]

# tmp <- paste0(sapply(unique(worcs_repos$owner), function(x){
#   owner_repos <- worcs_repos[worcs_repos$owner == x, , drop = FALSE]
#   paste0("\n    - ", x, "  ",
#          paste0("\n        + [", owner_repos$name, "](", owner_repos$url, ")  ", collapse = ""))
#   }),
#   collapse = "")

# invited <- read.table("https://raw.githubusercontent.com/cjvanlissa/resume/master/invited.csv", sep = ",", header = TRUE)
# invited <- invited[grepl("(worcs|workflow)", tolower(invited$Topic)), c("Institute", "Year", "City", "Country", "Date")]
# invited <- paste0(apply(invited, 1, function(x){paste0("\n    - ", x[1], " (", x[2], ")  ")}), collapse = "")
```

<!-- As of `r Sys.Date()`, these are indicators of the adoption of `worcs` by users: -->

<!-- 1. The preprint has been downloaded 1372 times, since being published on 31-05-2020 -->
<!-- 1. The paper in [Data Science](https://content.iospress.com/articles/data-science/ds210031) has been cited 13 times -->
<!-- 1. The `worcs` R-package has been downloaded r dl times from CRAN, since being published on 18-05-2020 -->
<!-- 1. The GitHub project has been forked r worcs_repo$network_count times, watched r worcs_repo$subscribers_count` times, and starred r worcs_repo$watchers times -->
<!-- 1. The lead author has given invited lecturegs on WORCS at: r invited -->
<!-- 1. WORCS is currently used in the following public itHub repositories (sorted by user): r tmp -->
